Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-03-27 documentation/userguide.tex
The sponge parameters can now be set via the probin file.

The \texttt{wdmerger} parameters of interest are all controlled through the \texttt{probin} file. 
These control the layout of the stars on the grid, the tagging options for refinement, and some other things. 
A \texttt{probin} file is composed of three Fortran namelists; a namelist is enclosed in 
\texttt{\&namelist ... /}. The \texttt{fortin} namelist controls the main system parameters. 
In the following list we describe the parameters; you can see their current defaults by 
examining \texttt{source/probin}.
\begin{itemize}
  \item \texttt{mass\_P}: mass of the primary white dwarf, in solar masses (real)
  \item \texttt{mass\_S}: mass of the secondary white dwarf, in solar masses (real; if less than zero, 
    then no secondary star will be generated, and the primary star will be loaded onto the grid at the 
    center of the domain)
  \item \texttt{nsub}: number of sub-intervals to divide a zone into when interpolating from the initial model (integer)
  \item \texttt{orbital\_kick}: whether or not to kick the stars with an orbital velocity corresponding to their 
    Keplerian rotation rate (logical; this only makes sense in the inertial reference frame with \texttt{castro.do\_rotation = 0})
  \item \texttt{damping}: whether or not to exert a constant damping force on the orbit (logical)
  \item \texttt{damping\_alpha}: strength of damping force (real)
  \item \texttt{bulk\_velx}: uniform velocity to give to all gas in the domain in the $x$-direction (real)
  \item \texttt{bulk\_vely}: uniform velocity to give to all gas in the domain in the $y$-direction (real)
  \item \texttt{bulk\_velz}: uniform velocity to give to all gas in the domain in the $z$-direction (real)
  \item \texttt{interp\_temp}: whether or not to take temperature as given when interpolating from our initial model (logical;
    if false, we will interpolate based on pressure)
  \item \texttt{maxTaggingRadius}: fractional size of the domain outside of which we won't perform any refinement (real)
\end{itemize}

>>>>

The \texttt{wdmerger} parameters of interest are all controlled through the \texttt{probin} file. 
These control the layout of the stars on the grid, the tagging options for refinement, and some other things. 
A \texttt{probin} file is composed of three Fortran namelists; a namelist is enclosed in 
\texttt{\&namelist ... /}. The \texttt{fortin} namelist controls the main system parameters. 
In the following list we describe the parameters; you can see their current defaults by 
examining \texttt{source/probin}.
\begin{itemize}
  \item \texttt{mass\_P}: mass of the primary white dwarf, in solar masses (real)
  \item \texttt{mass\_S}: mass of the secondary white dwarf, in solar masses (real; if less than zero, 
    then no secondary star will be generated, and the primary star will be loaded onto the grid at the 
    center of the domain)
  \item \texttt{nsub}: number of sub-intervals to divide a zone into when interpolating from the initial model (integer)
  \item \texttt{orbital\_kick}: whether or not to kick the stars with an orbital velocity corresponding to their 
    Keplerian rotation rate (logical; this only makes sense in the inertial reference frame with \texttt{castro.do\_rotation = 0})
  \item \texttt{damping}: whether or not to exert a constant damping force on the orbit (logical)
  \item \texttt{damping\_alpha}: strength of damping force (real)
  \item \texttt{bulk\_velx}: uniform velocity to give to all gas in the domain in the $x$-direction (real)
  \item \texttt{bulk\_vely}: uniform velocity to give to all gas in the domain in the $y$-direction (real)
  \item \texttt{bulk\_velz}: uniform velocity to give to all gas in the domain in the $z$-direction (real)
  \item \texttt{interp\_temp}: whether or not to take temperature as given when interpolating from our initial model (logical;
    if false, we will interpolate based on pressure)
  \item \texttt{maxTaggingRadius}: fractional size of the domain outside of which we won't perform any refinement (real)
  \item \texttt{sponge\_dist}: we can apply a sponge that damps the velocities starting at this fraction multiplied by the 
    distance from the center to the domain boundary (real)
  \item \texttt{sponge\_width}: smoothing width of the sponge; the sponge is fully applied at {\tt sponge\_dist} + {\tt sponge\_width},
    in the same coordinates (real)
  \item \texttt{sponge\_timescale}: the sponge decreases the velocity by a factor $1 / (1 + (\Delta t / t_s)$, where 
    $t_s$ is the {\tt sponge\_timescale} in seconds (real)    
\end{itemize}
